2-0-cube

### 2022-04-29 2-0-cube.Rmd
update Figure 1

The most common data cube using the three axes (time, latitude, longitude)  could be considered as taking snapshots of the space and stacking on time. Here we will define the spatio-temporal cube slightly differently with the three axes (time, site, variable), as illustrated in Figure \ref{fig:cube-def}. The time axis is the same in both versions, while the site axis now captures both latitude and longitude. Finally, variables are stacked on this space-time canvas, with one observation per site and time point. This notion is adopted to avoid using hypercubes when describing multivariate spatio-temporal data and is the conceptual framework behind \pkg{cubble}.

@@

```{r cube-def, echo = FALSE, fig.align="center", out.width = "50%", fig.cap = "An illustration of the conceptualised spatio-temporal cube with three axes: time, site, and variable."}
knitr::include_graphics(here::here("figures/cube-def.png"))
```

>>>>

The most common data cube using the three axes (time, latitude, longitude)  could be considered as taking snapshots of the space and stacking on time. Here we will define the spatio-temporal cube slightly differently with the three axes (time, site, variable), as illustrated in the leftmost cube in Figure \ref{fig:cube-def}. The time axis is the same in both versions, while the site axis now captures both latitude and longitude. Finally, variables are stacked on this space-time canvas, with one observation per site and time point. This notion is adopted to avoid using hypercubes when describing multivariate spatio-temporal data and is the conceptual framework behind \pkg{cubble}. With this conceptual model, operations on spatio-temporal data can be mapped to operations on the cube and the rest of Figure \ref{fig:cube-def} show examples of slicing on site, time, and variable.

@@

```{r cube-def, echo = FALSE, fig.align="center", out.width = "100%", fig.cap = "An illustration of the conceptual spatio-temporal cube with different slicing on time, site, and variable. For each axis, the slicing can be on a single value or a set of values."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.007.png"))
```
